---
title: "Celestial Object Classification"
author: 
  - Xiaoyang Wang
  - Ziang Zeng
output: 
  beamer_presentation:
    # toc: true
    slide_level: 2
    theme: "Madrid"
    # colortheme: "whale"
    citation_package: natbib
bibliography: ./references.bib
biblio-style: unsrt
biblio-title: References
header-includes:
  - \usepackage{bm}
  - \usepackage{booktabs}
#   - \setbeamertemplate{bibliography item}[text]
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = F,
                      warning = F)
```

```{r}
library(ggthemes)
library(tidyverse)
library(kableExtra)

mytheme <- theme(plot.title=element_text(face="bold.italic",
                                         size="14", color="brown"),
                 axis.title=element_text(face="bold.italic",
                                         size=10, color="brown"),
                 axis.text=element_text(face="bold", size=9,
                                        color="darkblue"),
                 panel.background=element_rect(fill="white",
                                               color="darkblue"),
                 panel.grid.major.y=element_line(color="grey",
                                                 linetype=1),
                 panel.grid.minor.y=element_line(color="grey",
                                                 linetype=2),
                 panel.grid.minor.x=element_blank(),
                 legend.position="right") 
```


## Outline

\tableofcontents

# Astronomical Challenge
Classifying celestial objects into stars, galaxies or quasars using their spectral characteristics.

# Data & Preprocessing
## Image of the celestial objects

\begin{figure}
\centering
\begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../data/GALAXY/GALAXY_1.jpg}
  \caption{Galaxy}
\end{minipage}\hfill
\begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../data/STAR/STAR_1.jpg}
  \caption{Star}
\end{minipage}\hfill
\begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../data/QSO/QSO_1.jpg}
  \caption{Qusar}
\end{minipage}
\end{figure}

## Image of the spectra

\begin{figure}
\centering
\begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../data/GALAXY_spec/GALAXY_spectrum_1.jpg}
  \caption{Galaxy Spec}
\end{minipage}\hfill
\begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../data/STAR_spec/STAR_spectrum_1.jpg}
  \caption{Star Spec}
\end{minipage}\hfill
\begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../data/QSO_spec/QSO_spectrum_1.jpg}
  \caption{Qusar Spec}
\end{minipage}
\end{figure}


## Metadata
```{r results='asis'}
df = read.csv("../data/metadata/clean_data.csv")[,-20]
vars = colnames(df)[c(-1, -18, -19)]
explanations = c("Right Ascension angle (at J2000 epoch)",
                 "Declination angle (at J2000 epoch)",
                 "Ultraviolet filter",
                 "Green filter",
                 "Red filter",
                 "Near Infrared filter",
                 "Infrared filter",
                 "Run Number",
                 "Rerun Number",
                 "Camera column",
                 "Field number",
                 "Unique ID used for optical spectroscopic objects",
                 "Object class",
                 "Redshift value based on the increase in wavelength",
                 "Plate",
                 "Modified Julian Date")

tab_exp = data.frame(vars, explanations)

kable(tab_exp, format = "latex", 
      booktabs = TRUE,
      caption = "Metadata of the celestial objects") %>%
  kable_styling(full_width = F, position = "center", font_size = 7)
```

## EDA
- Missing Values: 3

- Samples for each catagory: 33333

# Methodology
## Meta Data
- Explanatory Variables: u, g, r, i, z, redshift

- Response Variable: class
  - STAR: 0
  - GALAXY: 1
  - QSO: 2
  
- kNN: k = 3

- Decision Tree

## Convonlusional Neural Network

\begin{figure}
\centering
\begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../data/simple_cnn_visualization.png}
  \caption{a}
\end{minipage}
\end{figure}

## Voting Classifier

\begin{figure}
\centering
\begin{minipage}{0.6\textwidth}
  \centering
  \includegraphics[width=\linewidth]{./images/voting.png}
  \caption{b}
\end{minipage}
\end{figure}


# Results
## Metadata
```{r}
library(caret)
trainData <- read.csv("../data/metadata/train_metadata.csv")
testData <- read.csv("../data/metadata/test_metadata.csv")
```


```{r fig.cap='Confusion Matrix of Decision Tree', fig.height=5}
library(rpart)

treeModel <- rpart(class ~ ., data = trainData, method = "class")
predTree <- predict(treeModel, testData, type = "class")
cm_tree <- confusionMatrix(predTree, as.factor(testData$class))
cm_table <- as.table(cm_tree$table)
cm_df <- as.data.frame(cm_table)
colnames(cm_df) <- c('Reference', 'Prediction', 'Freq')

p1 <- ggplot(cm_df, aes(x = Reference, y = Prediction, fill = Freq)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "blue") +
  geom_text(aes(label = Freq), vjust = 1) +
  labs(title = "Confusion Matrix of Tree", x = "Actual Class", y = "Predicted Class") +
  mytheme

p1
```

## Metadata
```{r fig.cap='Confusion Matrix of kNN', fig.height=5}
library(class)
trainDataScaled <- scale(trainData[,-7]) # Assuming 'class' is the last column
testDataScaled <- scale(testData[,-7], 
                        center = attr(trainDataScaled, "scaled:center"), scale = attr(trainDataScaled, "scaled:scale"))

knnModel <- knn(train = trainDataScaled, test = testDataScaled, cl = trainData$class, k = 3)

cm_knn <- confusionMatrix(knnModel, as.factor(testData$class))
cm_table <- as.table(cm_knn$table)
cm_df <- as.data.frame(cm_table)
colnames(cm_df) <- c('Reference', 'Prediction', 'Freq')

p2 <- ggplot(cm_df, aes(x = Reference, y = Prediction, fill = Freq)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "blue") +
  geom_text(aes(label = Freq), vjust = 1) +
  labs(title = "Confusion Matrix of KNN", x = "Actual Class", y = "Predicted Class") +
  mytheme

p2
```

## Image of the celestial objects


## Image of the spectra


# Conclusions